### 2011-08-30 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.

@@

>>>>

\begin{figure}
  \caption{CH for \heu{Mutation}}
  \label{image-experiment-ch-for-mutation}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/ch-for-mutation}
\end{figure}

TODO odd are random, even are Glpk

TODO interpretation - Glpk as CH takes always one second, with simpler inputs almost always finds the optimum (thus the capping), with more complex is Random not that bad in the end

@@

\begin{figure}
  \caption{Ignoring Text Data}
  \label{image-experiment-ignore-text-data}
  \centering
    \includegraphics[width=\textwidth]{images/experiments/ignore-text-data}
\end{figure}
